---
title: "Life Expectancies"
author: "Denis Ryan"
date: "12 January 2018"
output:
  html_document: 
    toc: true
    toc_float: true
  
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Import Library
library(ggplot2)

#Path to gapminder data
gapminder <- read.table("https://raw.githubusercontent.com/resbaz/r-novice-gapminder-files/master/data/gapminder-FiveYearData.csv" ,sep = ",", header = TRUE)
```

## Introduction

We are going to present some results for the Life Expectancies and GDP of various nations.

### Life Expectancy by Continent

We examined life expectancy by continent and nation.

```{r lifexp, echo = FALSE}
g <- ggplot(data=gapminder, aes(x=year, y=lifeExp, colour=continent, group=country))
g + geom_line() + scale_y_log10() + facet_wrap(~continent) 
```

### GDP by Continent

We examined GDP by continent and nation.

```{r GDP, echo = FALSE}
g <- ggplot(data=gapminder, aes(x=year, y=gdpPercap, colour=continent, group=country))
g + geom_line() + scale_y_log10() + facet_wrap(~continent) 
```

### GDPvs Population by Continent

We examined GDP vs Population by continent and nation.

```{r GDPvspop, echo = FALSE}
g <- ggplot(data=gapminder, aes(x=pop, y=gdpPercap))
g <- g + geom_point(aes(colour=continent))
g + scale_y_log10() +scale_x_log10() + geom_density_2d() + facet_wrap(~continent) 
```

### Trying to divide gdp v pop from year to year...

As above so below

```{r GDPvspop2, echo = FALSE}
g <- ggplot(data=gapminder, aes(x=pop, y=gdpPercap))
g <- g + geom_point(aes(colour=continent))
g + scale_y_log10() +scale_x_log10() + geom_density_2d() + facet_wrap(~year) 
```

